---
title: "Analysis"
---

::: {.callout-warning}

This work is currently under progress.

:::


This page presents the preliminary analysis done on the dataset. 

Testing that running R works : 
```{r}
getwd()
```

First, we want to load the datasets : 

```{r}
library(foreign)
hhm = suppressWarnings(read.spss("data_management/data/raw/wave_1/KEN_2022_K-LSRH_v01_M_SPSS/hhm.sav",
    to.data.frame = TRUE))
dim(hhm)
hr = suppressWarnings(read.spss("data_management/data/raw/wave_1/KEN_2022_K-LSRH_v01_M_SPSS/hr.sav",
    to.data.frame = TRUE))
dim(hr)
rr = suppressWarnings(read.spss("data_management/data/raw/wave_1/KEN_2022_K-LSRH_v01_M_SPSS/rr.sav",
    to.data.frame = TRUE))
dim(rr)

wer = suppressWarnings(read.spss("data_management/data/raw/wave_1/KEN_2022_K-LSRH_v01_M_SPSS/wer.sav",
    to.data.frame = TRUE))
dim(wer)
```

[From the documentation](https://microdata.worldbank.org/index.php/catalog/6409/pdf-documentation), we have that : 

| **Data file** | **Cases** | **Variables** |
|---------------|-----------|---------------|
| **hhm**       | 45011     | 147           |
| This file contains data at the level of the individual for all household members |           |               |
| **hr**        | 9304      | 955           |
| This file contains household level information |           |               |
| **rr**        | 9285      | 939           |
| This file contains data at the representative respondent level |           |               |
| **wer**       | 7244      | 218           |
| This file contains data for the women empowerment module |           |               |

Which seems to confirm the good loading of the data. 

# Descriptive statistics. 

Doing some descriptive statistics, we have : 

```{r}

```

