---
title: "Descriptive Statisics"
---

::: {.callout-warning}
    This work is currently under progress.
:::

This page presents the preliminary analysis done on the dataset. 

# Loading the data

First, we want to load the different datasets : 

```{r}
library(foreign)
hhm = suppressWarnings(read.spss("data_management/data/raw/wave_1/KEN_2022_K-LSRH_v01_M_SPSS/hhm.sav",
    to.data.frame = TRUE))
hr = suppressWarnings(read.spss("data_management/data/raw/wave_1/KEN_2022_K-LSRH_v01_M_SPSS/hr.sav",
    to.data.frame = TRUE))
rr = suppressWarnings(read.spss("data_management/data/raw/wave_1/KEN_2022_K-LSRH_v01_M_SPSS/rr.sav",
    to.data.frame = TRUE))
wer = suppressWarnings(read.spss("data_management/data/raw/wave_1/KEN_2022_K-LSRH_v01_M_SPSS/wer.sav",
    to.data.frame = TRUE))
dim(rr)
dim(hr)
dim(hhm)
dim(wer)
```

[From the documentation](https://microdata.worldbank.org/index.php/catalog/6409/pdf-documentation), we have that : 

| **Data file** | **Cases** | **Variables** |
|---------------|-----------|---------------|
| **hhm**       | 45011     | 147           |
| This file contains data at the level of the individual for all household members |           |               |
| **hr**        | 9304      | 955           |
| This file contains household level information |           |               |
| **rr**        | 9285      | 939           |
| This file contains data at the representative respondent level |           |               |
| **wer**       | 7244      | 218           |
| This file contains data for the women empowerment module |           |               |

Which seems to confirm the good loading of the data. 

# Age distribution

If we interest ourselves in the first data file ``hhm`` wih information at the individual level of all surveyed household members, we can obtain the disribution of individuals across age. 

First, if we want the total distribution of individuals across age :

```{r}
maincol = "cyan3"
table(hhm$a4a_ageyrs)
plot(hhm$a4a_ageyrs,
    xlab = "Age", ylab = "Count",
    main = "Total distribution across age", 
    col = maincol)
```

If we want to plot genders separately. For males, we can do : 

```{r}
hhm_male = hhm[hhm$a4a_gender == "Male",]
plot(hhm_male$a4a_ageyrs,
    xlab = "Age", ylab = "Count",
    main = "Disribution of Males across age.",
    col = maincol)
```

For females, we have : 

```{r}
hhm_female = hhm[hhm$a4a_gender == "Female",]
plot(hhm_male$a4a_ageyrs,
    xlab = "Age", ylab = "Count",
    main = "Disribution of Females across age.",
    col = maincol)
```

Plotted together, we have : 

```{r}
library(ggplot2)
ggplot(hhm, aes(x = a4a_ageyrs, fill = a4a_gender)) +
                geom_bar(position = "dodge") +
                theme_minimal() +
                xlab("Age") +
                ylab("Count") +
                scale_fill_discrete(name = "Gender") +
                ggtitle("Age Distribution of Females and Males")
```

Or alternatively : 

```{r}
ggplot(hhm, aes(x = a4a_ageyrs, fill = a4a_gender)) + 
            stat_count() +
            theme_minimal() +
            xlab("Age") +
            ylab("Count") +
            scale_fill_discrete(name = "Gender") +
            ggtitle("Age Distribution by Gender")
```

# To come 

The further analysis is still planned : 

- Distribution of individuals in function of their nationality
- Distribution of individuals in function of their migration status

We are interested in the gap of consumption between Refugees and Resident.
We are therefore going to include other consumption variables in the following analysis.