---
title: "Descriptive Statisics"
format:
    pdf:
        toc: true
---

::: {.callout-warning}
    This work is currently under progress.
:::

This page presents the preliminary analysis done on the dataset. 

# Loading the data

First, we want to load the different datasets : 

```{r long_output}
library(foreign)
hhm = suppressWarnings(
    read.spss("data_management/data/raw/wave_1/KEN_2022_K-LSRH_v01_M_SPSS/hhm.sav",
    to.data.frame = TRUE))
hr = suppressWarnings(
    read.spss("data_management/data/raw/wave_1/KEN_2022_K-LSRH_v01_M_SPSS/hr.sav",
    to.data.frame = TRUE))
rr = suppressWarnings(
    read.spss("data_management/data/raw/wave_1/KEN_2022_K-LSRH_v01_M_SPSS/rr.sav",
    to.data.frame = TRUE))
wer = suppressWarnings(
    read.spss("data_management/data/raw/wave_1/KEN_2022_K-LSRH_v01_M_SPSS/wer.sav",
    to.data.frame = TRUE))
dim(rr)
dim(hr)
dim(hhm)
dim(wer)
```

[From the documentation](https://microdata.worldbank.org/index.php/catalog/6409/pdf-documentation), we have that : 

| **Data file** | **Cases** | **Variables** |
|---------------|-----------|---------------|
| **hhm**       | 45011     | 147           |
| This file contains data at the level of the individual for all household members |           |               |
| **hr**        | 9304      | 955           |
| This file contains household level information |           |               |
| **rr**        | 9285      | 939           |
| This file contains data at the representative respondent level |           |               |
| **wer**       | 7244      | 218           |
| This file contains data for the women empowerment module |           |               |

Which seems to confirm the good loading of the data. 

# Age distribution

If we interest ourselves in the first data file ``hhm`` wih information at the individual level of all surveyed household members, we can obtain the distribution of individuals across age. 

First, if we want the total distribution of individuals across age :

```{r}
maincol = "cyan3"
table(hhm$a4a_ageyrs)
plot(hhm$a4a_ageyrs,
    xlab = "Age", ylab = "Count",
    main = "Total distribution across age", 
    col = maincol)
```

Note that the last plotted value of the `hhm$a4a_ageyrs` variable is the `NA` value.
This behavior is reproduced in all following plots of this variable.

If we want to plot genders separately. For males, we can do : 

```{r}
hhm_male = hhm[hhm$a4a_gender == "Male",]
plot(hhm_male$a4a_ageyrs,
    xlab = "Age", ylab = "Count",
    main = "Distribution of Males across age.",
    col = maincol)
```

For females, we have : 

```{r}
hhm_female = hhm[hhm$a4a_gender == "Female",]
plot(hhm_male$a4a_ageyrs,
    xlab = "Age", ylab = "Count",
    main = "Distribution of Females across age.",
    col = maincol)
```

Plotted together, we have : 

```{r}
library(ggplot2)
ggplot(hhm, aes(x = a4a_ageyrs, fill = a4a_gender)) +
                geom_bar(position = "dodge") +
                theme_minimal() +
                xlab("Age") +
                ylab("Count") +
                scale_fill_discrete(name = "Gender") +
                ggtitle("Age Distribution of Females and Males") +
                scale_x_discrete(breaks = seq(min(as.numeric(hhm$a4a_ageyrs), na.rm = TRUE),
                    max(as.numeric(hhm$a4a_ageyrs), na.rm = TRUE), by = 5))
```

Or alternatively : 

```{r}
ggplot(hhm, aes(x = a4a_ageyrs, fill = a4a_gender)) + 
            stat_count() +
            theme_minimal() +
            xlab("Age") +
            ylab("Count") +
            scale_fill_discrete(name = "Gender") +
            ggtitle("Age Distribution by Gender") +
            scale_x_discrete(breaks = seq(min(as.numeric(hhm$a4a_ageyrs), na.rm = TRUE),
                max(as.numeric(hhm$a4a_ageyrs), na.rm = TRUE), by = 5))
```

# Nationality Distribution 

There are 12 different nationalities identified among the surveyed individuals. Represented with bars, we get : 

```{r}
plot(hhm$a4a_nationality,
    xlab = "Nationality", ylab = "Count",
    main = "Nationality",
    col = maincol)
```

To get an interactive pie chart, we could do  : 
````
```{{r}}
library(plotly)
plot_ly(data = hhm,
    labels = levels(hhm$a4a_nationality), 
    values = table(hhm$a4a_nationality),
    type = 'pie')
```
````

:::{.callout-warning}
Plotly does not render in pdf, but is available on the [website](https://www.paulogcd.com/Refugees_Kenya/analysis.html). 
I choose not to include a standard static pie chart due to small values making the format less viable for visualisation.
:::

# Migration status distribution

There are 8 possible values for migration status in the survey : 

```{r}
levels(hhm$a4a_migration)
```

However, it seems that three of them have 0 individuals registered : 

```{r}
table(hhm$a4a_migration)
```

Representing with bars, we get : 

```{r}
# Making the name shorter so that it is included in the plot :
levels(hhm$a4a_migration)[7] = "Asyleum seeker"
plot(hhm$a4a_migration,
    xlab = "Migration status", ylab = "Count",
    main = "Migration status",
    col = maincol)
```

To do an interactive pie plot, we could do : 

````
```{{r}}
plot_ly(data = hhm,
    labels = levels(hhm$a4a_migration), 
    values = table(hhm$a4a_migration),
    type = 'pie')
```
````

:::{.callout-warning}
Plotly does not render in pdf, but is available on the website. 
I choose not to include a standard static pie chart due to small values making the format less viable for visualisation.
:::

# To come 

The further analysis is still planned : 

- Joint distribution of the mentioned variables.

We are interested in the gap of consumption between Refugees and Resident.
We are therefore going to include other consumption variables in the following analysis.
